---
title: "tracksPlot: Tracks Plot"
author: "mixfruit"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{tracksPlot: Tracks Plot}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Introduction

The `tracksPlot` function creates tracks plots for visualizing genomic or transcriptomic data. This specialized visualization displays multiple tracks of data aligned along a common axis, allowing for the comparison of different data types or conditions.

## Usage

```r
tracksPlot(
  data,
  tracks,
  group_by = NULL,
  color_by = NULL,
  ...
)
```

## Arguments

- `data`: A data frame containing tracks data
- `tracks`: A vector of track names to plot
- `group_by`: Group tracks by a variable
- `color_by`: Variable to color the tracks by
- `...`: Additional arguments passed to other methods

## Example

### Using Built-in Data

Let's demonstrate `tracksPlot` using example data:

```{r, eval=FALSE}
library(scVisual)

# Load example data (hypothetical)
# tracks_data <- readRDS(system.file("extdata", "htdata.RDS", package = "scVisual"))

# Create tracks plot
# tracksPlot(tracks_data, tracks = c("track1", "track2", "track3"))
```

### Customizing the Plot

You can customize the tracks plot by adjusting colors, grouping, and other visual properties:

```{r, eval=FALSE}
# Create customized tracks plot
# tracksPlot(
#   tracks_data,
#   tracks = c("track1", "track2", "track3"),
#   group_by = "condition",
#   color_by = "sample",
#   title = "Genomic Tracks Comparison"
# )
```

## Output

The function returns a ggplot2 object, which can be further customized using ggplot2 functions:

```{r, eval=FALSE}
# Create tracks plot and customize
# p <- tracksPlot(tracks_data, tracks = c("track1", "track2", "track3"))
# p + 
#   theme_minimal() +
#   labs(subtitle = "Multi-omic Tracks")
```

## Tips

- Use `tracksPlot` to compare multiple data tracks along a common axis
- The function works best with 2-5 tracks for clear visualization
- Use `group_by` and `color_by` to enhance comparisons across different categories
- Adjust track heights and spacing for optimal readability
